Advancing spatially explicit fisheries management with age-structured species distribution models

### 2025-02-27 paper/paper-word.qmd
reorg

format: 
  pdf:
    keep-tex: true
    template-partials: 
      - title.tex
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
author:
  - name: Eric Ward
  - name: Nick Tolimieri
    affiliations:
    - Conservation Biology Division, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanographic and Atmospheric Administration, 2725 Montlake Blvd E, Seattle WA 98112

@@

We thank Owen Liu and XX reviewers for constructive comments on the manuscript.

>>>>

format: 
  docx: default

author:
  - name: Eric Ward
  - name: Nick Tolimieri
    affiliations:
    - Conservation Biology Division, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanographic and Atmospheric Administration, 2725 Montlake Blvd E, Seattle WA 98112

@@

We thank Owen Liu and Chris Jordan for constructive comments on the manuscript.
